---
title: "HW_1"
author: "Ray"
date: "2023-10-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Q1

(b)statements is right,while (a) is wrong.We can easily know X1 and X2 are convex set.As the intersection defines, the intersectin of X1 and X2 is convex.

## Q2

(a)statement is right for the reason that Quadratic functions is convex only if A>=0,and so that when t=0,epo f ={(x,t)|f(x)<0},epi f is convex set.

## Q3

(a)is right for example f(x)=-x^2 when x in[-1,2],it is a nonconvex function has a unique minimum -4.(b) is wrong,for example convex funtion x^2 plus concave function -2*x^2 is -x^2,which is a concave function.

## Q4

(a) is convex for the reason  a twice differentiable f is e^x >0 for x on R.
(b) is quasiconvex for the reason that the Hessian Matrix of f >0,which ∇2f (x)>0.
(c) is concave function because the Hessian Matrix is[(0,1/x2^2),(-1/x2^2,2/x2^3)]<0.

## Q5

(a) has optimal value 0.6 when (x1,x2)=(0.4,0.2),which means optimal set is(0.4,0.2)
(b) is equal to maxinize(x1+x2) which has no exact value because x1,x2 has infinite value,so it has no minization.
(c) has optimal value 0 when x1=0, x2>=1,the optimal set is (0,x2)when x2>1.
(d) has optimal value 1/3 when optimal set is(1/3,1/3)
(e) has optimal value 1/2 when optimal set is(1/2,1/6)
```{r}
library(ggplot2)

# 创建数据框
df <- data.frame(x = c(0, 1/2), y = c(1,0))
df_2<-data.frame(x=c(0,1),y=c(1/3,0))

# 绘制线性规划图
ggplot(df_2,aes(x, y))+ geom_abline(intercept = 1, slope = -2)+
  geom_line() +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0) +
  xlim(0, 2) +
  ylim(0,2) +
  xlab("x") +
  ylab("y")

library(Rglpk)

obj_1 <-c(1,1)
obj_2 <-c(-1,-1)
obj_3 <-c(1,0)

mat<-matrix(c(2,1,1,3,1,0,0,1),nrow = 4,byrow = TRUE)
dir<-c(">=",">=",">=",">=")
rhs<-c(1,1,0,0)

max<-FALSE
Rglpk_solve_LP(obj_1,mat,dir,rhs,max)
```




## Q6

(a) is a convex optimization problem because f0(x), f1(x), f2(x), .., fn(x) are convex functions and h1(x), h2(x),.., hn(x)
are affine functions.
(b) is a convex optimization problem because fi(.)’s are increasing functions,and fi(.)^2's second derivative>0,so fi(x)^2 is convex function,so it is a convex optimization.
(c) is not a convex optimization problem because min{fi(x)}is not a convex function,for example ,min{x^2,(x-1)^2} is not a convex function ,so (c) is not a convex optimization problem.
(d) is not a convex optimization problem because fi(x) are convex function,so -fi(x) is a nonconvex function, it dont satisfy the format of the optimization problem.
(e) is a convex optimization problem because sum of wi*fi(x) when wi>0 is also a convex function,so it is a convex optimization.

## Q7

(c) is a convex optimization reformulation of the original problem (4).(a)and(d) is not the original problembecause fi(x)<=0 is not equal to fi(x)==0.(b) is not the original problem because it's answer will always greater than zero.

## Q8

ϕ(u) is a convex function for the reason when |u| ≤ M which means u belongs to[-M,M],u^2 is a convex function and when |u|>M,M(2|u| − M) is also a convex function because M >0.And ϕ(u) is a continuous function so ϕ(u) is a convex function. And aT(i) x − bi is a Composition with affine functions,so ϕ(aT(i) x − bi) is a convex function, so do sum of the ϕ(aT(i) x − bi)  convex fucntion is.As a result, the problem is a convex optimization.



## Q9

Write the R code for solving the following optimization problem:

below is the solution

```{r ,warning=FALSE}
library(CVXR)

Sigma = matrix(c(4,2,0,2,6,2,0,2,2),nrow=3,ncol=3,byrow=TRUE)

w<-Variable(nrow(Sigma))

pro<-Problem(Minimize(quad_form(w, Sigma)),constraints=list(w>=0,sum(w)==1))

result<-solve(pro)

w <- as.vector(result$getValue(w)/sum(abs(result$getValue(w))))

print(w)
```


